Note for Scattering Amplitude Computation

### 2025-04-24 Note/Note.tex
New

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{cancel}
\usepackage{graphicx}
\setlength{\parskip}{0.3em}
\setlength{\parindent}{0pt}
% 使用系统字体，需要 XeLaTeX 或 LuaLaTeX 编译
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{xcolor}
\usepackage{float}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\left\langle #1 \right\rangle}
\newcommand{\doubleavg}[2]{\left\langle #1 \right\rangle\!\left\langle #2 \right\rangle}
\newcommand{\inavg}[2]{\langle #1 \rangle\! [#2]}
\newcommand{\rinavg}[2]{[#1]\!\langle #2 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\begin{document}

@@

>>>>

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{cancel}
\usepackage{graphicx}
\setlength{\parskip}{0.3em}
\setlength{\parindent}{0pt}
% 使用系统字体，需要 XeLaTeX 或 LuaLaTeX 编译
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{xcolor}
\usepackage{float}
\usepackage{caption}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\doubleavg}[2]{\left\langle #1 \right\rangle\!\left\langle #2 \right\rangle}
\newcommand{\inavg}[2]{\langle #1 \rangle\! [#2]}
\newcommand{\rinavg}[2]{[#1]\!\langle #2 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\begin{document}

@@

\section{3-point building block}
We have known that the on-shell 3-point amplitudes can be completely determined by the little group scaling, according to the following formulas
\begin{align*}
    A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
    \quad & h_1+h_2+h_3 < 0 \\[0.5em]
    A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
    \quad & h_1+h_2+h_3 > 0
\end{align*}
Because of the specialty of this kind of 2 site gauge theory, there are no direct interaction between gauge boson and scalar, so there are only two kinds of 3-point amplitudes.
\begin{itemize}
    \item 2 scalar 1 gauge boson
    \begin{equation*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\mdavg{23}{31}}{\avg{12}}
    \end{equation*}
    \item 3 gauge boson
    \begin{equation*}
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\mdavg{45}{53}}
    \end{equation*}
\end{itemize}
If there are no exceptions, 1 and 2 always represent the antiscalar and scalar respectively, other number represent the gauge boson.

\section{Gauge boson sector}
In this section, we will show how to build the gauge boson scattering. Because there's no direct interaction between gauge boson 1 and gauge boson 2, so we only need to compute one of them.
And although we have already known the formulas for MHV color-ordered amplitudes for gluon scattering -- Parke-Talyor Formula 
\begin{equation*}
    A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\mdavg{n-1,n}{n1}}
\end{equation*}
also for the anti-MHV amplitudes
\begin{equation*}
    A[\cdots,i^+,\cdots,j^+,\cdots]=\frac{[ij]^4}{[12][34]\cdots[n-1,n][n1]}
\end{equation*}
Here, we will give an concrete example to show how to use BCFW to compute the 4-point amplitudes $A[3^+,4^+,5^-,6^-]$

\begin{figure}[H]
    \centering
    \includegraphics{4ptg.pdf}
    \caption*{4pt gluon}
\end{figure}
We choose the $[3,4\rangle$ shift, and it has been proved that $[+,+\rangle$ shift is valid
\begin{gather*}
    \sket{\hat{3}}=\sket{3}-z\sket{4},\qquad \qquad \aket{\hat{4}}=\aket{4}+z\aket{3}\\
    \aket{\hat{3}}=\aket{3}, \qquad \sket{\hat{4}}=\sket{4}.
\end{gather*}
The first diagram can be evaluated 
\begin{equation*}
    A_1=\frac{[\hat{3}\hat{I}]^3}{[\hat{I}6][6\hat{3}]}\times\frac{1}{s_{36}}\times\frac{\avg{5\hat{I}}^3}{\mdavg{\hat{I}\hat{4}}{\hat{4}5}}
\end{equation*}
The point here is that 
\begin{equation*}
    \text{Pole position}:\quad \hat{P}_{34}^2=0=\avg{36}[6\hat{3}]\quad \Rightarrow  \quad [6\hat{3}]=0,
\end{equation*}
for the similar reason, we can obtain $[\hat{I}6]=[6\hat{3}]=0$, so we conclude that the left part
\begin{equation*}
    \frac{[\hat{3}\hat{I}]^3}{[\hat{I}6][6\hat{3}]}=0
\end{equation*}
so the first channel is vanishing.

The second diagram can be similarly evaluated
\begin{align*}
    A_2&=\frac{\avg{\hat{I}6}^3}{\mdavg{6\hat{3}}{\hat{3}\hat{I}}}\times\frac{1}{s_{36}}\times\frac{[\hat{I}\hat{4}]^3}{[\hat{4}5][5\hat{I}]}\\
       &=\frac{[34]^3}{[34][45][56][61]}
\end{align*}
From this, we can conclude that the color-ordered amplitude equals to
\begin{equation*}
    A[3^+,4^+,5^-,6^-]=\frac{[34]^3}{[34][45][56][63]}.
\end{equation*}
and it can also be expressed by angle brackets interchangeably
\begin{equation*}
    A[3^+,4^+,5^-,6^-]=\frac{\avg{56}^3}{\mdavg{34}{45}\!\mdavg{56}{63}}
\end{equation*}
Then, 5-point , 6-point can be recursively computed by using BCFW recursion relation.

\section{SQCD like sector}
First we explain the color decomposition in this sector by 4 point amplitude $\Phi^\dagger V_1V_1\Phi$
    \begin{figure}[htbp]
        \centering
        \begin{minipage}[t]{0.32\textwidth}
            \centering
            \includegraphics[width=\linewidth]{sch.pdf}
            \caption*{s channel}
        \end{minipage}
        \hfill
        \begin{minipage}[t]{0.32\textwidth}
            \centering
            \includegraphics[width=\linewidth]{uch.pdf}
            \caption*{u channel}
        \end{minipage}
        \hfill
        \begin{minipage}[t]{0.32\textwidth}
            \centering
            \includegraphics[width=\linewidth]{tch.pdf}
            \caption*{t channel}
        \end{minipage}
    \end{figure}

    The color factor can be written respectively as following
    \begin{equation*}
        r_s=\mathrm{Tr}[\Phi_2^\dagger T^{a_3}T^{a_4}\Phi_1],\,r_u=\mathrm{Tr}[\Phi_2^\dagger T^{a_4}T^{a_3}\Phi_1],\,
        r_t=\mathrm{Tr}[\Phi_2^\dagger [T^{a_3},T^{a_4}]\Phi_1]
    \end{equation*}
    We can easily obtain a similar Jacobbi relation
    \begin{equation*}
        r_t=r_s-r_u
    \end{equation*}
    Then we can accomplish the color decomposition and define the corressponding color-ordered amplitudes.

    For example, in the 4pt. case, the full amplitude can be decomposed to the following form
        \begin{align*}
            \mathcal{A}_4(\Phi^\dagger V_1V_1\Phi)&=A_s r_s+A_u r_u+A_t r_t\\
            &=A_s r_s+A_u r_u+A_t(r_s-r_u)\\
            &=(A_s+A_t)r_s+(A_u-A_t)r_u
        \end{align*}
        The two subamplitudes can be defined as color-ordered amplitude with order \textcolor{red}{[1,2,3,4]} and 
        \textcolor{red}{[1,2,4,3]} respectively.
        Of course, for the type $\Phi^\dagger(nV_1)\Phi$ and $\Phi (nV_2) \Phi^\dagger$, we can do the same thing to define the color-ordered amplitudes.

    We start from the 4-point color-ordered $A[1,2,3^+,4^-]$ again
    \begin{center}
    \begin{minipage}{0.45\textwidth}
        \begin{align*}
        A[1,2,3^+,4^-] &= \sum_{h}
        \end{align*}
        \end{minipage}
        \hspace{-3em}
        \begin{minipage}{0.45\textwidth}
        \raisebox{-1em}{\scalebox{0.8}{\includegraphics{4pt1.pdf}}}
        \end{minipage}
    \end{center}

    $\hspace{13.7em} =\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.1.pdf}}}+\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.2.pdf}}}$
